Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-26 paper/paper.Rmd
move case study vis after execution, add new section "should new methods be added to existing ML ecosystems?"

# Application in a Case Study

...
<!-- FIXME: @alex: do you want to see more into here? -->

The partition plots shown in the following are also used in the case study in section \@ref(sec:case-study).

Besides the required arguments of the \pkg{mlr3} superclass `Task`, `TaskClassifST` / `TaskRegrST` classes also require the following arguments passed via a named list `extra_args`:

- `coordinate_names`: Names of the features which represent the spatial coordinates.
  This is automatically inferred when a `sf` object is passed.
- `coords_as_features`: Whether the coordinates should be used as features during modeling.
  By default coordinates are not used as predictors.
- `crs`: The coordinate reference system of the data. Valid inputs are PROJ4 strings or EPSG codes in the format `ESPG: <code>`.

# equal to `tsk("ecuador")`
b = mlr3::as_data_backend(ecuador)
b$hash = "_mlr3_tasks_ecuador_" # optional
task = TaskClassifST$new(
  id = "ecuador", b, target = "slides", positive = "TRUE",
  extra_args = list(
    coordinate_names = c("x", "y"), coords_as_features = FALSE,
    crs = "+proj=utm +zone=17 +south +datum=WGS84 +units=m +no_defs") # EPSG:32717
)
```

Due to space limitations only the first two folds are plotted.

@@

@@

At first all necessary R packages are loaded and a lower verbosity is set to keep the output tidy.
Also a seed is set for deterministic execution and the \pkg{mlr3spatiotempcv} built-in task `"ecuador"` is loaded via `tsk()`.
Next, the random forest learner (`lrn("classif.ranger")`) is initialized with default hyperparameters and the prediction type set to `"probability"` due to the binary response variable.
A set of commonly used learners is available in package \pkg{mlr3learners} [@mlr3learners], including the random forest implementation after @ranger.

```{r prepare}
library("mlr3")
library("mlr3spatiotempcv")
library("mlr3learners")

task = tsk("ecuador")

@@

@@

@@

<!-- missing: Guidelines how to choose a resampling method -->
While various spatiotemporal resampling methods exists nowadays to account for spatiotemporal autocorrelation in modeling, there is still lots of uncertainties which method should be used for which dataset.
The answer to this question is not trivial and while there will most likely never be an easy answer to this, this topic needs to be discussed in more detail so that users feel more certain about their actions.
One option could be a checklist of dataset characteristics showing which characteristics make a certain dataset more suitable for specific methods.
This could then help users to make an appropriate and objective decision which resampling method might be a good fit for their dataset.

<!--mention missing spatiotemporal buffering method -->
At the time of writing this article, there is no buffering methods which operates in the spatiotemporal domain.
Though we encourage users generally to check out the supported methods in the \pkg{mlr3spatiotempcv} package directly to potentially discover new methods which might have been added to the package in the meantime.

>>>>

@@

Besides the required arguments of the \pkg{mlr3} superclass `Task`, the `TaskClassifST` / `TaskRegrST` classes from package \pkg{mlr3spatiotempcv}  also require the following arguments during construction which must be passed via a named list `extra_args`:

- `coordinate_names`: Names of the features which represent the spatial coordinates.
  This is automatically inferred when a `sf` object is passed.
- `coords_as_features`: Whether the coordinates should be used as features during modeling.
  By default coordinates are not used as predictors.
- `crs`: The coordinate reference system of the data. Valid inputs are PROJ4 strings or EPSG codes in the format `ESPG:<code>`.

At first all necessary R packages are loaded and a lower verbosity is set to keep the output tidy.
Also a seed is set for deterministic execution and the \pkg{mlr3spatiotempcv} built-in task `"ecuador"` is loaded via `tsk()`.

# equal to `tsk("ecuador")`
b = mlr3::as_data_backend(ecuador)
b$hash = "_mlr3_tasks_ecuador_" # optional
task = TaskClassifST$new(
  id = "ecuador", b, target = "slides", positive = "TRUE",
  extra_args = list(
    coordinate_names = c("x", "y"), coords_as_features = FALSE,
    crs = "EPSG:32717")
)
```

@@

Next, the random forest learner (`lrn("classif.ranger")`) is initialized with default hyperparameters and the prediction type set to `"probability"` due to the binary response variable.
A set of commonly used learners is available in package \pkg{mlr3learners} [@mlr3learners], including the random forest implementation after @ranger.

```{r prepare}
library("mlr3learners")

@@

## Fold visualization

Finally, we visualize the folds that were used during performance estimation making use of the generic `autoplot()` function in package \pkg{mlr3spatiotempcv}.
Due to space limitations only the first two folds are shown.

@@

## Should new methods be added to existing ML ecosystems or made available in a new package?

@@

<!-- missing: Guidelines how to choose a resampling method -->
The \pkg{mlr3spatiotempcv} package is the first package to bundle and categorize spatiotemporal resampling methods in R.
While various spatiotemporal resampling methods exists nowadays to account for spatiotemporal autocorrelation in modeling, there is still lots of uncertainty which method should be used for which dataset.
The answer to this question is not trivial and while there will most likely never be an easy answer to this, this topic needs to be discussed in more detail so that users feel more certain about their actions.
One option could be the proposal of a dataset characteristic checklist showing which characteristics make a certain dataset more suitable for specific methods.
This could then help users to make an appropriate and objective decision which resampling method might be a good fit for their dataset.

<!--mention missing spatiotemporal buffering method -->
At the time of writing this article, there is no buffering method which operates in the spatiotemporal domain.
We encourage readers of this article to check out the supported methods in the latest released version of the \pkg{mlr3spatiotempcv} package directly to potentially discover new methods which might have been added to the package in the meantime.
